Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
Fix an hbox
Random shit

\begin{itemize}
\item \libpurple makes a distinction between ``IMs'' and ``chats''; \libmotmot
does not.  (In particular, IMs are defined as a direct two-person communication
only, whereas chats are an overarching category that can involve one, two, or
more users.) \libpurple takes in different arguments for its IM-related and its
chat-related functions

@@

We faced a challenge when writing the \verb`enter` function.  This function is a
callback responsible for allowing a user to enter a chat.  Due to the structure
of \libmotmot, the only information passed into \verb`enter` as an argument is
an internal handle, and we need create some sort of external handle.  We solved
this by creating a global variable, \verb`GLOBAL_ACCOUNT`, which represents the
account that a user first logs in under, and we associate our external handle
with this \verb`GLOBAL_ACCOUNT`.  Though this ``works'' if a user only signs in
with on eaccount, this breaks when a user decides to sign in with multiple
accounts at once (something that \libpurple allows), and should be addressed in
future versions.

>>>>

\begin{itemize}
\item \libpurple makes a distinction between ``chats'' and ``IMs''; \libmotmot
does not.  (In particular, IMs are defined as a direct two-person communication
only, whereas chats are an overarching category that can involve one, two, or
more users.) \libpurple takes in different arguments for its IM-related and its
chat-related functions

@@

We faced a challenge when writing the \verb`enter` function.  This function is a
callback responsible for allowing a user to enter a chat.  Due to the structure
of \libmotmot, the only information passed into \verb`enter` as an argument is
an internal handle, and we need create some sort of external handle.  We solved
this by creating a global variable, \verb`GLOBAL_ACCOUNT`, which represents the
account that a user first logs in under, and we associate our external handle
with this \verb`GLOBAL_ACCOUNT`.  Though this ``works'' if a user only signs in
with one account, this breaks when a user decides to sign in with multiple
accounts at once (something that \libpurple allows), and should be addressed in
future versions.
